Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-21 cav2017/cav2017.tex
use lower case consistently for precision underscript

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Our synthesis problem}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
The synthesis problem we are trying to solve is the following:
find a digital controller $K$ (see Eq.~\ref{eq:controlaction})
that makes the closed-loop system safe for 
initial state $x_0$, reference signal $r_k$ and input $u_k$
as defined in Sec.~\ref{ssec:safety}. 
We consider non-deterministic initial states within a specified range
and the reference signal to be 0 (\addtodo{refer to wherever this is explained initially}).
Then, when mapping back to the notation used for describing the general architecture 
of the program synthesizer, the controller $K$ denotes $P$ and 
$(x_0, u_k)$ represents $x$. 
While the controller's precision $\langle I_C,F_C\rangle$ is given, 
we can vary the plant's precision $\langle I_p,F_p\rangle$ such that 
$\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I_c,F_c \rangle$.

>>>>

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Our synthesis problem}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
The synthesis problem we are trying to solve is the following:
find a digital controller $K$ (see Eq.~\ref{eq:controlaction})
that makes the closed-loop system safe for 
initial state $x_0$, reference signal $r_k$ and input $u_k$
as defined in Sec.~\ref{ssec:safety}. 
We consider non-deterministic initial states within a specified range
and the reference signal to be 0 (\addtodo{refer to wherever this is explained initially}).
Then, when mapping back to the notation used for describing the general architecture 
of the program synthesizer, the controller $K$ denotes $P$ and 
$(x_0, u_k)$ represents $x$. 
While the controller's precision $\langle I_c,F_c\rangle$ is given, 
we can vary the plant's precision $\langle I_p,F_p\rangle$ such that 
$\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I_c,F_c \rangle$.
